Software Citation Principles

### 2016-07-20 sc-principles/rebuttal/rebuttal.tex

From my personal perspective, this is a very good contribution, which addresses one of the most important topics in the ``citation'' domain, i.e. software citation. I totally agree with the reviewers about the readability of the paper, and I think this paper will deserve publication in PeerJ CS.

However, there are some aspects that should be clarified in the revision. In particular:
}

\begin{enumerate}
\item  \textbf{Comment:}
%\textbf{1. Comment:}
\emph{I would like to see a new section that describes the presentation of these principles at FORCE 2016, and includes also a summary of the most important outcomes derived from the discussion the authors have done during the conference. Did such outcomes change some of the principles and/or other claims in this paper?}

\textbf{Our response:}
We have added some additional description of these activities in Section 2,
and also a new appendix that records the feedback and discussion following
the FORCE2016 workshop and presentation. The workshop and feedback following
presentation to the broader FORCE11 community led to some edits to the use
cases and discussion, but not the principles themselves.

### 2016-07-20 sc-principles/software-citation-principles.tex
rearranged use cases in appendix

The group gathered members (see Appendix~\ref{app:wg_members}) in April and May 2015,
and then began work in June, with a number of meetings
and some off-line work by group members to gather materials documenting existing
practices in member disciplines; gather materials from workshops and other reports;
review those materials, identifying overlaps and differences; and subsequently draft an initial version of this document.
The draft Software Citation Principles document was discussed in a day-long workshop and presented at the FORCE2016 Conference~\cite{force2016} in April 2016.
Members of the workshop and greater FORCE11 community gave feedback, which we recorded here in Appendix~\ref{app:force16-feedback}.
This discussion led to a second, final version.
We also plan to initiate a follow-on working group that will work with stakeholders to ensure that these principles impact the research process.

@@

The research wants to publish about a version of software they have produced.
A key part of this use case is to be able to connect the given narrative to a specific version of the software in questions and connect that in large story.

@@

@@

@@

This is the case where a researcher is using some software to perform an analysis, either of a physical sample or of data.
The researcher needs to know which version was used, for example in case a bug was fixed.
Note that knowing the software and its version is not sufficient to determine the ``conditions'' of the analysis, but they are essential.

>>>>

The group gathered members (see Appendix~\ref{app:wg_members}) in April and May 2015,
and then began work in June, with a number of meetings
and some off-line work by group members to gather materials documenting existing
practices in member disciplines; gather materials from workshops and other reports;
review those materials, identifying overlaps and differences; and subsequently draft an initial version of this document.
The draft Software Citation Principles document was discussed in a day-long workshop and presented at the FORCE2016 Conference~\cite{force2016} in April 2016.
Members of the workshop and greater FORCE11 community gave feedback, which we recorded here in Appendix~\ref{app:force16-feedback}.
This discussion led to some changes in the use cases and discussion, although the principles themselves were not modified.
We also plan to initiate a follow-on working group that will work with stakeholders to ensure that these principles impact the research process.

@@

\subsection{Publisher wants to publish a software paper}

\niemnote{add description}

@@

\subsection{Evaluator or funder wants to evaluate contributions of a researcher}

\niemnote{add description}

@@

\subsection{Repository wants to publish mixed data\slash software packages}

\niemnote{add description; came from \url{https://github.com/force11/force11-scwg/issues/128}}
Domain and institutional data repositories have both data and software
artifacts, and want to link these together in a provenance trace that can
be cited. Sometimes the software is a separately identified artifact, but at
other times software is included inside of data packages, and the researcher
wants to cite the combined product.

\subsection*{Use cases not adopted in the table:}

\niemnote{this seems the same as use case 1}
The research wants to publish about a version of software they have produced.
A key part of this use case is to be able to connect the given narrative to a specific version of the software in questions and connect that in large story.

@@

\niemnote{Is this distinct from 6? Or should it be a new one?}
This is the case where a researcher is using some software to perform an analysis, either of a physical sample or of data.
The researcher needs to know which version was used, for example in case a bug was fixed.
Note that knowing the software and its version is not sufficient to determine the ``conditions'' of the analysis, but they are essential.
